---
title: "O2 Group Project"
author: "Yangjia Huang"
date: "2017Äê12ÔÂ7ÈÕ"
output: html_document
---
#Introduction
Nowadays, air polution has become a more and more critical issues for people living in Madrid. Especially, the density of NO2 in air has been proved to have strong relation with many different kinds of disease. Therefore, this study to aim to analyze the relation between the density of NO2 and weather factors, other air polutants, using lineary regression model. The study has showed that factors such as density of CO, TOL, TCH, SO2, PM2.5, EBE have a significantly positive impact on the density of NO2. Possible explaination could be these polutants are derived from fossil buring, such as traffic in the city. Factors such as avg wind speed have significantly negative impact on the density of NO2. 

#Data Source


#Library
```{r, include = T}
library(cowplot)
library(data.table)
library(Hmisc)
library(corrplot)
library(ggplot2)
```
#Step 1: Importing Raw Data
1.creating a vector with all the file names using the format -- hourly_data_<year>_<month>

```{r, include = T}
years <- c(11:16)
months <- c(1:12)
file_names <- c(1:72)
file_index <- 1
for(i in years){
  for(j in months){
    file_name <- paste('hourly_data',i,j,sep='_')
    file_names[file_index] <- file_name
    file_index <- file_index+1
  }
}

file_names
```

2.importing data from the file source(path), using the file name vector created in the past step. At the same time, creating new columns for year and month. Treat Null as 0.
```{r, include = T}
file_names
all_data <- data.frame()

for(i in file_names){
  path <- paste('C:/MBD/STATISTICAL PROGRAMMING - R/Pratice/Group Assignment/workgroup data/',i,'.csv',sep='')
  data <- read.csv(file = path,stringsAsFactors = T, sep=',')
  data[is.na(data)] = 0
  year_index <- strsplit(i,'_')[[1]][3]
  month_index <- strsplit(i,'_')[[1]][4]
  data <- cbind(rep(year_index,nrow(data)),rep(month_index,nrow(data)),data)
  all_data <-rbind(all_data,data)
}
str(all_data)
```

3.renaming colnames for year and month. the newly created columns do not have their own column names. Here in this step, they will be assigned their own column names.
```{r, include = T}
colnames(all_data) <- c('year','month',colnames(all_data)[3:7])
str(all_data)
```


4.saving data for next step
```{r, include = T}
write.csv(all_data,file="aggregated_data.csv",row.names = F,col.names = T)
```

#Step 2: Merging polutant data with weather data. This step is aim to create a data.frame that contains weather data and daily polutant data.
1.importing data: reading data from last step and importing weather data.
```{r, include = T}
all_data <- read.csv(file = 'C:/MBD/STATISTICAL PROGRAMMING - R/Pratice/Group Assignment/aggregated_data.csv', stringsAsFactors = T, sep = ',')
str(all_data)

weather <- read.csv(file = 'C:/MBD/STATISTICAL PROGRAMMING - R/Pratice/Group Assignment/weather.csv', stringsAsFactors = T, sep = ',')
str(weather)
```

2.building data.frame containing name and index number of parameters
```{r, include = T}
parameters <- c(rep(0,17))
parameters <- data.frame(parameters)
rownames(parameters) <- c(1,6,7,8,9,10,12,14,20,30,35,37,38,39,42,43,44)
parameters[,'parameters'] <- c('SO2','CO','NO','NO2','PM2.5','PM10','NOx','O3','TOL','BEN','EBE','MXY','PXY','OXY','TCH','CH4','NMHC')
parameters
```

3.Creating a dataframe--all data_by day,that has all the daily average values of each pollutant
```{r, include = T}
all_data_day <- aggregate(all_data$value, list(all_data$year,all_data$month,all_data$day,all_data$parameter),mean, na.rm = T)
all_data_day <- cbind(paste0(rep(20,nrow(all_data_day)),all_data_day$Group.1),all_data_day[2:5])
all_data_day <- cbind(paste(all_data_day[,1],all_data_day[,2],all_data_day[,3],sep='-'),all_data_day[,4:5])
all_data_day$`paste(all_data_day[, 1], all_data_day[, 2], all_data_day[, 3], ` <- as.Date.factor(all_data_day$`paste(all_data_day[, 1], all_data_day[, 2], all_data_day[, 3], `)
colnames(all_data_day) <- c('date','parameter','value')
str(all_data_day)
```
4.Ungroup all_data_day, assign to a list called new_all_data_day. Each element of the list is a dataframe containing information just for that pollutant
```{r, include = T}
new_all_data_day <- split.data.frame(all_data_day,f = as.factor(all_data_day$parameter))
for(i in 1:12){
  colnames(new_all_data_day[[i]]) <- c('date','1',unique(new_all_data_day[[i]][,2]))
  new_all_data_day[[i]] <-new_all_data_day[[i]][,c(1,3)]
  
}
str(new_all_data_day)
```
5.Renaming weather data.frame. Notice that due to the encoding setting, some of the column names in the weather data table are not correctly encoded. This step will rename all these column names.
```{r, include = T}
colnames(weather) <- c("date","temp_avg","temp_max","temp_min","precipitation","humidity", "wind_avg_speed")
str(weather)
```

6.Join weather data.frame with all dataframes in new_all_data_day by Key.value = date. Save the final result in data.frame: weather_pollutants.
```{r, include = T}
weather[,1] <- as.Date.factor(weather[,1])
for(i in new_all_data_day){
  weather <- merge.data.frame(weather,i,by ='date')
}
str(weather)

colnames(weather) <- c(colnames(weather)[1:7],parameters[colnames(weather)[8:19],])

weather_pollutants <- weather

head(weather_pollutants)
```

7.saving the result
```{r, include = T}
write.csv(weather_pollutants,file = 'weather_pollutants.csv')
```

#Step 3: Plotting data to see that for each variable in a time series, does it show a pattern or trend in the time series.

1. Importing data from previous step and call it WePo(weather and Pollutant)
```{r, include = T}
WePo <- read.csv(file = "C:\\MBD\\STATISTICAL PROGRAMMING - R\\Pratice\\Group Assignment\\weather_pollutants.csv", sep = ',' )
WePo$date <- as.Date(WePo$date)
WePo <- as.data.table(WePo)
WePo$humidity <- as.numeric(WePo$humidity)
str(WePo)
head(WePo)
```

2.plotting data, using ggplot
```{r, include = T}
plotting <- function(mydata,i){
  i <- as.integer(i)
  ggplot(data = mydata, aes(date, mydata[[i]])) + geom_point(color = '#4682B4', fill = '#4682B4')+ ylab(colnames(mydata)[i]) + ggtitle(paste0(colnames(mydata)[i],'~','date')) + theme_light()+theme(panel.border = element_blank(), plot.title = element_text(hjust = 0.5, size = 20), axis.title = element_text(size = 14))
}

for(i in 3:ncol(WePo)){
print(plotting(WePo, i))
  }
```

As it is observed, most of the variables do not show a pattern on their distributions over time.

#Step 4. Regression

1.loading weather_pollutant.csv and assign it to WePo
```{r, include = T}
WePo <- read.csv(file='C:/MBD/STATISTICAL PROGRAMMING - R/Pratice/Group Assignment/weather_pollutants.csv', sep = ',')
```

2.Create a Corelation Matrix to see which variables are most important to NO2
```{r, include = T}
corrplot.mixed(cor(WePo[,-c(1,2)]),order = 'hclust',upper = 'circle',lower = 'number', title = 'NO2 ~ All Variables',diag = 'u', tl.pos = 'lt', number.cex = 0.3, tl.cex = 0.5,tl.srt = 35, mar = c(0,0,1.1,1))
```

3.Select those variables that are most important to NO2(larger circles), and assign them to a data.frame -- sub-WePo. Then create another corelattion plot to see which of the selected variables(candidates of independent variables) have strong corelation.
```{r, include = T}
sub_WePo <- WePo[,c(15,8,17,10,11,16,19,9,13,18)]
corrplot(cor(sub_WePo), order = 'hclust', method = 'number', title = 'Selected Independent Variables', tl.cex = 0.5,tl.srt = 35, mar = c(0,0,1.1,1), number.cex = 0.5)
```

4.To avoid multilinear problem, here remove independent variables that have coefficient index over 0.8, removing BEN. Again, do a new corrplot to check.

5. Transform variable NO to variable NO_lag(NO value in one day before), test correlation between new variable NO_lag and CO2 & NO2.
```{r, include = T}
sub_WePo_lag <- cbind(sub_WePo[-1, ],sub_WePo[-nrow(sub_WePo),'NO'])
colnames(sub_WePo_lag) <- c(colnames(sub_WePo_lag)[-11],'NO_lag')

corrplot(cor(sub_WePo_lag[,-c(3,5)]), order = 'hclust', method = 'number', title = 'Selected Independent Variables(without BEN)', tl.cex = 0.5,tl.srt = 35, mar = c(0,0,1.1,1), number.cex = 0.5)

GGally::ggpairs(sub_WePo_lag[,-c(3,5)], lower = list( continuous = wrap("points",size = 0.5, alpha = 0.05)), upper = list(continous = wrap("cor", alpha = 1)), title = "Selected Independent Variables(without BEN)") + theme(axis.text = element_text(size = 5), text = element_text(size = 10))

cor(data.frame(WePo$NO2[-1],sub_WePo_lag$NO_lag))
cor(data.frame(sub_WePo_lag$CO,sub_WePo_lag$NO_lag))
```

The result show that NO_lag have a strong corelation with NO2, at the same time NO_lag has a lower coefficient index with CO, compared with NO.

6.linear Model
```{r, include = T}
model_data <-cbind(WePo$NO2[-1],sub_WePo_lag[,-c(3,5)])
colnames(model_data) <- c("NO2",colnames(model_data)[2:ncol(model_data)])
regression <- lm(NO2~ . , model_data)
summary(regression)
```

7.Residual Analysis£ºResidual vs Fitted Plot | Residual Boxplot | Residual Histogram | QQ Plot
```{r, include = T}
p1<-ggplot(regression, aes(.fitted, .resid))+geom_point(color = '#4682B4', size =0.2)
p1<-p1+stat_smooth(method="loess", color = "#0000CD")+geom_hline(yintercept=0, col="red", linetype="dashed")
p1<-p1+xlab("Fitted values")+ylab("Residuals")
p1<-p1+ggtitle("Residual vs Fitted Plot")+theme_light()+theme(panel.border = element_blank(), plot.title = element_text(hjust = 0.5, size = 10), axis.title = element_text(size = 8))

p2 <- ggplot(regression, aes(y = regression$residuals, x = ' '))+geom_boxplot(stat = 'boxplot', position = 'dodge', outlier.colour = 'red', outlier.size = 0.2, outlier.shape = 1, color =  '#4682B4')
p2 <- p2 + ylab('residuals') + xlab('SalePrice')
p2 <- p2 + ggtitle('Residual Boxplot') + theme_light()+theme(panel.border = element_blank(), plot.title = element_text(hjust = 0.5, size = 10), axis.title = element_text(size = 8))

p3 <- ggplot(regression, aes(regression$residuals))+geom_histogram(fill = '#4682B4')+geom_freqpoly(color = "#00BFFF", size = 0.5)
p3 <- p3 + geom_vline(xintercept = mean(regression$residuals), color = 'red', linetype = "dashed" )
p3 <- p3 + xlab('Residuals') + ggtitle('Residual Histogram') + theme_light()+theme(panel.border = element_blank(), plot.title = element_text(hjust = 0.5, size = 10), axis.title = element_text(size = 8))

p4 <- ggplot(regression, aes(sample = regression$residuals)) + geom_qq(geom = 'point', color ='#4682B4', size = 0.2 )
p4 <- p4 + ggtitle('QQ Plot')+ theme_light()+theme(panel.border = element_blank(), plot.title = element_text(hjust = 0.5, size = 10), axis.title = element_text(size = 8))

plots <- list(rvfPlot=p1, boxPlot=p2, histPlot=p3, qqPlot=p4)


plot_grid(plotlist = plots)
```

¢Ùthe residual plot are randomly dispersed around the horizontal axis. However, they show some kind of non-linear relation.

¢Úthe residual boxplot shows some outliers

¢Ûthe residual histogram shows the distribution of the residual are approximately normal distribution

¢Üthe variance seem constant

#Conclusion
The lineary model has showed that factors such as density of CO, TOL, TCH, SO2, PM2.5, EBE have a significantly positive impact on the density of NO2. Possible explaination could be these polutants are derived from fossil buring, such as traffic in the city. Factors such as avg wind speed and O3 have significantly negative impact on the density of NO2. 